Plots

### 2025-02-27 src/plots.Rmd
Use PCCC abbrv for plots:

# Models cases
raw_models <- df_raw %>% select(ends_with("_cghr10"), -physician_cghr10)
for (mcol in colnames(raw_models)) {
    m <- raw_models[[mcol]]
    cat(paste0(
        str_replace_all(mcol, models_format), " Predicted Cases (", 
        length(unique(na.omit(m))), " CODs): ",
        length(m) - sum(is.na(m) | is.null(m)),
        "\n"
    ))
}

@@

# Models cases
models <- df %>% select(ends_with("_cghr10"), -physician_cghr10)
for (mcol in colnames(models)) {
    m <- models[[mcol]]
    cat(paste0(
        str_replace_all(mcol, models_format), " Predicted Cases (", 
        length(unique(na.omit(m))), " CODs): ",
        length(m) - sum(is.na(m) | is.null(m)),
        "\n"
    ))
}

# Models agreed cases
models_agree <- df %>%
    filter(is_agreed == TRUE) %>%
    select(ends_with("_cghr10"), -physician_cghr10)
for (mcol in colnames(models_agree)) {
    m <- models_agree[[mcol]]
    cat(paste0(
        str_replace_all(mcol, models_format), " Agreed Predicted Cases (", 
        length(unique(na.omit(m))), " CODs): ",
        length(m) - sum(is.na(m) | is.null(m)),
        "\n"
    ))
}
```

@@

# Plot perf for pccc by age groups
fig_pccc <- plot_perf(
    df_long %>%
        mutate(
            age_label = case_when(
                age_name == "Adult"
                    ~ paste0(age_name, "\n12+ Years\n(n=", n_adult, ", ", round(perc_adult), "%)"),
                age_name == "Child"
                    ~ paste0(age_name, "\n28 Days to 11 Years\n(n=", n_child, ", ", round(perc_child), "%)"),
                age_name == "Neonate"
                    ~ paste0(age_name, "\n<28 Days\n(n=", n_neo, ", ", round(perc_neo), "%)"),
                .default = age_name
            ) %>%
                factor(., levels = unique(.) %>% sort %>% rev)
        ),
    calc_pccc,
    group = "age_label",
    x_title = "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
    text_mid_vjust = 3,
    sort_group = F,
    x_limits = c(0.2, 0.8),
    x_expand = waiver()
)

@@

# Plot adult perf for pccc by cod
fig_pccc_cod_adult <- plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
    x_title =  "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
    text_mid_vjust = -1,
    text_scale = 0.8
)

@@

# Plot child perf for pccc by cod
fig_pccc_cod_child <- plot_perf(
    df_long %>% filter(age == "child"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Child, 28 Days to 11 Years (n=", n_child, ")"),
    x_title =  "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
    text_scale = 0.95
)

@@

# Plot neo perf for pccc by cod
fig_pccc_cod_neo <- plot_perf(
    df_long %>% filter(age == "neo"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Neonatal, <28 Days (n=", n_neo, ")"),
    x_title =  "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
    text_mid_vjust = 3,
    text_end_size = 2.25,
    text_scale = 0.95
)

@@

# Plot perf trend over age ranges
fig_pccc_age <- plot_perf_trend(
    df_long %>%
        mutate(
            age_range = str_replace(age_range, " ", "\n") %>%
                factor(., levels = age_levels)
        ),
    title = "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
    text_scale = 0.9
)

>>>>

# Models cases
raw_models <- df_raw %>% select(ends_with("_cghr10"), -physician_cghr10)
for (mcol in colnames(raw_models)) {
    m <- raw_models[[mcol]]
    cat(paste0(
        mcol, " Predicted Cases (", 
        length(unique(na.omit(m))), " CODs): ",
        length(m) - sum(is.na(m) | is.null(m)),
        "\n"
    ))
}

@@

# Models cases
models <- df %>% select(ends_with("_cghr10"), -physician_cghr10)
for (mcol in colnames(models)) {
    m <- models[[mcol]]
    cat(paste0(
        mcol, " Predicted Cases (", 
        length(unique(na.omit(m))), " CODs): ",
        length(m) - sum(is.na(m) | is.null(m)),
        "\n"
    ))
}

# Models agreed cases
models_agree <- df %>%
    filter(is_agreed == TRUE) %>%
    select(ends_with("_cghr10"), -physician_cghr10)
for (mcol in colnames(models_agree)) {
    m <- models_agree[[mcol]]
    cat(paste0(
        mcol, " Agreed Predicted Cases (", 
        length(unique(na.omit(m))), " CODs): ",
        length(m) - sum(is.na(m) | is.null(m)),
        "\n"
    ))
}
```

@@

# Plot perf for pccc by age groups
fig_pccc <- plot_perf(
    df_long %>%
        mutate(
            age_label = case_when(
                age_name == "Adult"
                    ~ paste0(age_name, "\n12+ Years\n(n=", n_adult, ", ", round(perc_adult), "%)"),
                age_name == "Child"
                    ~ paste0(age_name, "\n28 Days to 11 Years\n(n=", n_child, ", ", round(perc_child), "%)"),
                age_name == "Neonate"
                    ~ paste0(age_name, "\n<28 Days\n(n=", n_neo, ", ", round(perc_neo), "%)"),
                .default = age_name
            ) %>%
                factor(., levels = unique(.) %>% sort %>% rev)
        ),
    calc_pccc,
    group = "age_label",
    x_title = "PCCC",
    text_mid_vjust = 3,
    sort_group = F,
    x_limits = c(0.2, 0.8),
    x_expand = waiver()
)

@@

# Plot adult perf for pccc by cod
fig_pccc_cod_adult <- plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
    x_title =  "PCCC",
    text_mid_vjust = -1,
    text_scale = 0.8
)

@@

# Plot child perf for pccc by cod
fig_pccc_cod_child <- plot_perf(
    df_long %>% filter(age == "child"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Child, 28 Days to 11 Years (n=", n_child, ")"),
    x_title = "PCCC",
    text_scale = 0.95
)

@@

# Plot neo perf for pccc by cod
fig_pccc_cod_neo <- plot_perf(
    df_long %>% filter(age == "neo"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Neonatal, <28 Days (n=", n_neo, ")"),
    x_title = "PCCC",
    text_mid_vjust = 3,
    text_end_size = 2.25,
    text_scale = 0.95
)

@@

# Plot perf trend over age ranges
fig_pccc_age <- plot_perf_trend(
    df_long %>%
        mutate(
            age_range = str_replace(age_range, " ", "\n") %>%
                factor(., levels = age_levels)
        ),
    title = "PCCC",
    text_scale = 0.9
)
